Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-10 paper/disc20clustering.tex
wip

Finally, we note the possibility of improvement. The algorithm CREP~\cite{repartition-disc} requires $(2+\epsilon)$-augmentation to guarantee the competitive ratio independent of $\ell$.
In contrast, our construction shows that the linear term $\ell$ is inevitable if the augmentation is smaller than $1+1/3$.

@@

	The cost of \OPT is lower-bounded by the cost of serving $\sigma_I$ and the cost of serving $\sigma_E$.
	While serving these requests, $\OPT$ may perform migrations, and we account for them in both parts: we separately bound $\OPT$ by $\OPT(\sigma_I) + \OPT(M)$ and $\OPT(\sigma_E) + \OPT(M)$.
	Combining those bounds and using the relation between the maximum and the average gives us
	\begin{align*}
		\OPT&\geq \max\{\OPT(\sigma_I) + \OPT(M), \OPT(\sigma_E) + \OPT(M)\}\\
		&\geq (\OPT(\sigma_I) + \OPT(M)) / 2 + (\OPT(\sigma_E) + \OPT(M)) / 2.
	\end{align*}

@@

>>>>

Finally, we note the possibility of improvement. The algorithm CREP~\cite{repartition-disc} requires $(2+\epsilon)$-augmentation to guarantee the competitive ratio independent of $\ell$.
In contrast, our construction shows that the linear term $\ell$ is inevitable if the augmentation is smaller than~$1+1/3$.

@@

	The cost of \OPT is lower-bounded by the cost of serving $\sigma_I$ and the cost of serving $\sigma_E$.
	While serving these requests, $\OPT$ may perform migrations, and we account for them in both parts: we separately bound $\OPT$ by $\OPT(\sigma_I) + \OPT(M)$ and $\OPT(\sigma_E) + \OPT(M)$.
	Combining those bounds and using the relation between the maximum and the average, we obtain the bound
	\begin{align*}
		\OPT&\geq \max\{\OPT(\sigma_I) + \OPT(M), \OPT(\sigma_E) + \OPT(M)\}\\
		&\geq (\OPT(\sigma_I) + \OPT(M)) / 2 + (\OPT(\sigma_E) + \OPT(M)) / 2.
	\end{align*}

@@

\maciek{"	I.e., $ C^t_{\set{u,v}} = \lambda$." is too short for a sentence. Merge with the previous sentence?}
